Formal Paper Draft

### 2022-01-13 PaperDraft.Rmd
including additional sammon results

```{r, echo = FALSE}
mds1 <- readRDS("2021-10-18_simulationsmaller_mds_list.RDS")
tsne1 <- readRDS("2021-10-18_simulationsmaller_tsne_list.RDS")

#### Generate a table of values to assess efficacy of detections -----------------#
df2list <- tsne1
df3list  <- mds1
#note - these will give values per run - so we need to take a look across the simulations

@@

#mean detection rates
#mean detection rates
Category <- c("Correctly Identified Influential", "Correctly Non-Identified Non-Influential")
TSNE <- c(round(mean(ci1),3), round(mean(cni1),3))
MDS <- c(round(mean(ci2),3), round(mean(cni2),3))
Isomap <- c("","")
Sammon <- c("","")
temp <-rbind(Category,TSNE, MDS, Isomap, Sammon)
colnames(temp) <- Category
kable(temp)

@@

The Carnegie Classification is typically based on a scaled version of the data due to the presence of outlier institutions on several metrics.  In particular, some institutions spend a great deal of expenditures on research compared to others, so the actual CC is based on two indices generated using Principal Component Analysis on the ranked data (Cite Harmon, Kosar).

For this analysis, we instead look at scaled versions of the unranked data in part to assess whether or not some of the relative extreme points appear as influential relative to other universities in the group.

@@

## NEED TO STANDARDIZE THE DATA FIRST (MAKE UNITLESS)
CCscale <- CC2015_filter %>% lapply(scale) %>% as_tibble()

out <- MultiPermanova(CCscale, maptype = "MDS")
```

>>>>

```{r, echo = FALSE}
#mds1 <- readRDS("2021-10-17_simulationlarger_mds_list.RDS")
mds1 <- readRDS("2022-01-12_simulationlarger_mds_list.RDS")
tsne1 <- readRDS("2021-10-17_simulationlarger_tsne_list.RDS")
sammon1 <- readRDS("2022-01-12_simulationlarger_Sammon_list.RDS")

@@

#MDS
ci3 <- sapply(df4list, correctInfluence)
cni3 <- sapply(df4list, correctNonInfluence)

#mean detection rates
#mean detection rates
Category <- c("Correctly Identified Influential", "Correctly Non-Identified Non-Influential")
TSNE <- c(round(mean(ci1),3), round(mean(cni1),3))
MDS <- c(round(mean(ci2),3), round(mean(cni2),3))
Isomap <- c("","")
Sammon <- c(round(mean(ci3),3), round(mean(cni3),3))
temp <-rbind(Category,TSNE, MDS, Isomap, Sammon)
colnames(temp) <- Category
kable(temp)

@@

The Carnegie Classification is typically based on a ranked set of institutional features due to the presence of outlier institutions on several metrics.  In particular, some institutions spend a great deal of expenditures on research compared to others, so the actual CC is based on two indices generated using Principal Component Analysis on the ranked data (Harmon, et al 2018; Kosar and Scott, 2017). This has a similar effect on the results as to a log transform or standardization process (Kosar and Scott, 2017).

CC2015_filter <- CC2015 %>% filter(BASIC2015 %in% c(15,16,17)) %>% dplyr::select(PDNFRSTAFF, S.ER.D, NONS.ER.D, FACNUM, HUM_RSD, STEM_RSD, OTHER_RSD, SOCSC_RSD)
#perplexity = 30

#include a plot of the 2015 Carnegie Classification

Rank <- c(1:5)
Name <- rep("Name", 5)

kable(cbind(Rank, Name), col.names = c("", "MDS"))

Initially, we investigate scaled versions of the unranked data in part to assess whether or not some of the relative extreme points appear as influential relative to other universities in the group.  Interestingly, even with some scaling performed, we see that for MDS, the institutions that are surfaced as "influential" are those that seem to fit the bill of being different from the average profile.  The institution with the largest F statistic is Harvard University, followed by:

**INSERT A PCP of the institutions identified as significant**

### Without Scaling or Ranking

Without scaling or ranking the data at all, the results look even more interesting.

@@

## NEED TO STANDARDIZE THE DATA FIRST (MAKE UNITLESS)
#CCscale <- CC2015_filter %>% lapply(scale) %>% as_tibble()

#out <- MultiPermanova(CCscale, maptype = "MDS")
```
